
\vspace{.2cm}
\noindent\textbf{\emph{Subproject 2: Normative Issues (Literary Theory / G\"ottingen}}
\vspace{.1cm}

\noindent This subproject intends to approach (Q2) by examining the influence of \emph{literary appreciation} on what a work of fiction prescribes us to imagine. In particular, we want to contribute to answering the following question:

\vspace{-.2cm}
\begin{quote}
(Q2.1) Does appreciation influence what literary works of fiction
prescribe us to imagine, and if so, how?
\end{quote}
\vspace{-.2cm}

\noindent The subproject has three interrelated parts. The first part asks for the influence of literary appreciation on the determination of fictional \emph{content}, i.e. on \emph{what} to imagine. This part is mainly analytic in that it tries to uncover the structure and force of arguments in favor of the thesis that appreciation does play a role in the determination of content. The second part is constructive, arguing that the appreciation of certain \emph{narrative-structural} features of literary fictions presupposes an imaginative involvement of a certain \emph{kind}; in this part, we therefore aim at spelling out the influence of literary appreciation on \emph{how} to imagine a particular content. The third part is mainly speculative in focusing on implications of both ventures for the very notion of prescribed imaginings.

In asking for the influence of literary appreciation on what to imagine, the \textbf{first part} of the subproject starts with a very general notion of aesthetic appreciation. According to a widely held view, aesthetic appreciation aims at the appraisal of aesthetic merit, and works of art have aesthetic merit in so far as they offer for intrinsically valuable experiences (Budd 1995; Goldman 2006). This conception of aesthetic appreciation can easily be applied to literary fictions. Take the notorious debate about whether there are ghosts in H. James' \emph{The Turn of the Screw} (Currie 1991). The claim that there are ghosts that are in contact with the children supposedly makes for a (more) scary reading than the claim that there are no ghosts in the story world, but rather a deluded governess. Other things being equal, the fact that the story is scary amounts to a merit-constituting property of a ghost story. Hence, it seems that the claim that `in the fiction\textsubscript{W}, \emph{p}, makes for a more scary reading of work \emph{W}' counts in favor of the claim `in the fiction\textsubscript{W}, \emph{p}'. Generalizing over this particular case, we get something like the following hypothesis: 

\vspace{-.2cm}
\begin{quote}
(H2.1) A content-ascribing interpretation \emph{I\textsubscript{1}} is
(other things being equal) better than its alternative
\emph{I\textsubscript{2}}, if imagining in accordance with it leads to
an intrinsically more valuable experience. (Cf. Goldman 1995, 102)
\end{quote}
\vspace{-.2cm}

\noindent However, both the details and the validity of (H2.1) are far from clear
and need to be carefully scrutinized. For instance, the example
discussed suggests that whether the dispositional quality of `allowing
for a scary reading' counts as a merit-constituting property of a work
depends on the genre (cf. Walton 1970). Suppose that we read \emph{The
Turn of the Screw} as a psychological novella instead.{~ }Doesn't, in
the context of this reading, the claim that in the fiction, there is a
deluded governess (\emph{q}), rather than ghosts, constitute the more
rewarding reading experience, and hence counts in favor of the claim `in
the fiction\textsubscript{W}, \emph{q}? Also, (H2.1) seems to imply that
aesthetic experiences can be compared (cf. Budd 1995, 42f., on the
incommensurability of aesthetic value). And, given that the
\emph{appropriateness} of experiences of aesthetic value depends on the
quality of the interpretations the experiences are based on, (H2.1)
moreover seems to imply that the appropriateness of experiences of
aesthetic value depends on the degree of value ascribed by the
interpretation. Both implications of (H2.1) are clearly problematic. Our
first sub-question, then, becomes:

\vspace{-.2cm}
\begin{quote}
(Q2.1a)  Does the realization of aesthetic merit help to determine
which of two (otherwise equally well supported) content-ascribing
interpretations \emph{I\textsubscript{1}} and \emph{I\textsubscript{2}}
is to be preferred, and if so, how?
\end{quote}
\vspace{-.2cm}

\noindent (H2.1) is concerned with the rather simple case of two alternative
interpretations which are \emph{ex hypothesi} equally well supported in
all other relevant respects. However, interpretations can be more or
less convincing according to several different criteria (Strube 1992).
For instance, content-ascribing interpretations may be judged according
to the purely formal criterion of how many (important) textual features
they explain (F\o{}llesdal et al. 2008). Now, suppose that we have two
(otherwise equally well supported) incompatible interpretations,
\emph{I\textsubscript{1}} and \emph{I\textsubscript{2}}, such that
\emph{I\textsubscript{1}} ascribes a merit-constituting property as
explained above (say, `in the fiction\textsubscript{W}, \emph{p}'),
while \emph{I\textsubscript{2}} ascribes another property (say, `in the
fiction\textsubscript{W}, \emph{q}'), thereby having greater explanatory
scope with respect to other (important) properties of the work than
\emph{I\textsubscript{1}}. Which one should be preferred? Our second
sub-question therefore becomes:

\vspace{-.2cm}
\begin{quote}
(Q2.1b)  Do merit-constituting properties trump other criteria for
content ascriptions, and if so, how?
\end{quote}
\vspace{-.2cm}

\noindent In the next step, we turn to another notion of appreciation, namely
literary appreciation more narrowly construed, and its putative
influence on content-ascriptions/prescriptions to imagine. Interpreters
are not always guided by the goal of enabling readers to undergo
experiences which are intrinsically valuable (Shusterman 1978). For
instance, they may also aim at `historical interpretation' (cf. Olsen
2004, 142; on different goals of interpretation in literary studies, cf.
Kindt/M\"uller 2003, 212; K\"oppe/Winko 2013). Proponents of historical
interpretation take seriously the idea that works of literary fiction
are historical artifacts and try to uncover the ways the work was
intended to be read by its historical audiences (or the ways it was
actually read by these audiences). As we shall argue, appreciating a
work of fiction as a historical artifact certainly amounts to
appreciating the work \emph{as} a work of fiction. Historical
interpretation is not meant to merely \emph{use} the work, say, in order
to gain historical knowledge about the world (cf. Eco 1999, 35ff.), but
rather the work itself and its properties are at the focus of interest.
Thus it seems fair to say that historical interpretation amounts to a
form of literary appreciation, and is in the business of uncovering
\emph{literary merit} (cf. Lamarque 2009, 171). Our third sub-question
therefore becomes:

\vspace{-.2cm}
\begin{quote}
(Q2.4)  How are we to decide between two (incompatible)
interpretations, \emph{I\textsubscript{1}} and
\emph{I\textsubscript{2}}, of work W, such  that
\emph{I\textsubscript{1}} involves the claim that `in the
fiction\textsubscript{W}, \emph{p}', thereby giving rise to literary
merit \emph{M\textsubscript{1}}, and  \emph{I\textsubscript{2}}
involves the claim that `in the fiction\textsubscript{W}, \emph{q}',
thereby giving rise to literary merit \emph{M\textsubscript{2}}?
\end{quote}
\vspace{-.2cm}

\noindent In working on part one of the subproject, we need to keep two
methodological points in mind. Firstly, one may be tempted to claim that
(Q 1.1), (Q 1.2) and (Q 1.3) need to be answered on a case to case
basis. Literary interpretation is often regarded as holistic insofar as
one has to trade the total package of pros and cons of
\emph{I\textsubscript{1}} off against the total package of pros and cons
of \emph{I\textsubscript{2}} \ldots \emph{I\textsubscript{n}} (K\"oppe
2008b, 86f.). The results of {Subproject 3 (\#Tom\#)} will hopefully
contribute to our understanding of the matter. But even if holism gives
us the correct picture with respect to content-ascriptions (both
\emph{de iure} and \emph{de facto}), we certainly want to know what
types of reasons guide, and ought to guide, our decisions in typical
cases. Secondly, maybe there is no best interpretation to be had, but
rather only optimal ones (in the sense of Currie 2003, 293). We turn to
some implications this may have for the notion of prescribed imaginings
below, as part three of this subproject.

\textbf{Part two} of the current subproject asks for the influence of
literary appreciation on \emph{how} to imagine. It does so by
identifying three narrative-structural features the appreciation of
which will be argued to make special claims on the imagination. Thus a
case will be made that certain narrative structural features not only
normatively constrain the content of our imaginings but also \emph{how}
to imagine it. We focus on three such features, namely \emph{unreliable
narration}, the distinction between \emph{telling vs. showing}, and
\emph{internal focalization}.

Unreliable narration comes in many forms (cf. Kindt 2008; K\"oppe/Kindt
2014, ch. 4.4). One form involves the reader's misinformation about the
contours of the story world. Readers of Bierce's \emph{An Occurrence at
Owl Creek Bridge} are told that the protagonist escapes from a life
threatening situation, only to learn later on in the story that the
escape was nothing but the hallucinations of the dying man (St\"uhring
2011). This narrative strategy, then, centrally involves a distinction
between what is the case in the fiction and what is but \emph{seemingly}
the case in the fiction. However, we surely cannot say that only the
former is what is important to appreciating the work. For, arguably,
appreciating the short story involves that you first faithfully follow
the protagonist's hallucinations (without knowing that they are but
hallucinations, that is), that you gain hope and be awaked, and probably
disappointed, in the end. So, what do we have here in terms of
prescriptions to imagine? In previous work, we have proposed to
distinguish between prescriptions to imagine and \emph{prima facie}
prescriptions to imagine (K\"oppe/Kindt 2011). Readers are, in other
words, mislead by the story concerning what it is that they are
prescribed to imagine. This solution leaves untouched the idea that
prescriptions to imagine establish fictional facts. But it does not seem
to capture the idea that, in order to appreciate the story in accordance
with its narrative strategy, one actually \emph{needs} to be mislead
concerning what is the case in the fiction. The work, as it were,
prescribes us to imagine what it does not prescribe us to imagine. This
needs explanation. A variant of this account has been proposed by
St\"uhring (2011) who claims that passages of unreliable narration give
readers a reason to imagine what (as might only be seen from an all
things considered perspective) is not the case in the fiction. Again,
however, the details are far from clear; in particular, it is not clear
how the accounts relate to what has been identified as a major
functional effect of the story, i.e. its propensity of elicit a
particular emotionally qualified imaginative response (cf. K\"oppe 2012b).
Our research question thus becomes:

\vspace{-.2cm}
\begin{quote}
(Q2.5)  How can we accommodate that in certain cases of unreliable
narration literary fictions seem  to prescribe emotionally qualified
imaginings that, moreover, do not establish fictional facts?
\end{quote}
\vspace{-.2cm}

\noindent Besides unreliable narration, we shall examine two more
narrative-structural features of literary fictions and argue that they
have a bearing on the \emph{way} the works ask us to imagine what is the
case in the fiction. The second feature under consideration is
\emph{internal focalization}, i.e. the telling of a narrative from the
perspective of one of its characters (Genette 1980, 185ff.;
Klauk/K\"oppe/Onea 2012). Take the sentences `Peter looked out of the
window. The cars were green.' Presumably, readers are supposed to
imagine that the focal character, Peter, sees the green cars, or that
the cars looked green to Peter. Accordingly, we have a necessary
condition for internal focalization, spelled out in terms of prescribed
imaginings. We might, very roughly, represent it like this: `If a
passage of text \emph{t} with a content \emph{c} of a fictional
narrative is internally focalized through a character \emph{C}, then
readers are prescribed by \emph{t} to imagine that `\emph{C} perceives
\emph{c}'.' It is a common assumption, however, that the appreciation of
internally focalized passages of text not only involves grasping what is
the case in the story world. These passages rather invite you to
imaginatively perceive the situation \emph{from the character's
perspective} (Lindemann 1987, 6; Habermas 2006, 505; Stanzel 2008, 16).
The passages, in other words, invite you to put yourself, imaginatively,
in the character's shoes. Thus for the Peter-case, you are invited to
imagine seeing the green cars. But again, we need to spell out the
details. Recently, the related claim that point of view shots in
cinematic fiction prompt readers to imagine seeing things from the
character's point of view has been put to criticism (Choi 2005), and a
similar case can be made for the effects of internal focalization, it
seems. Hence, our research question is:

\vspace{-.2cm}
\begin{quote}
(Q2.6) Do passages of internal focalization prescribe us to imagine
the content of what is said from  the point of view of the focal
character, and if so, how? 
\end{quote}
\vspace{-.2cm}

\noindent A similar case will be made for the notorious distinction between
\emph{telling vs. showing} modes of presentation in a narrative
(Klauk/K\"oppe 2014a; Klauk/K\"oppe 2014c; Klauk/K\"oppe 2015). The gist of
passages of \emph{showing} seems to be that readers are invited to
\emph{vividly} imagine what the text is about. But this is not more than
the beginning of an account of the narrative mode of showing. Obviously,
any passage of narrative fiction could be said to invite a rich and
multifaceted, hence vivid, imaginative engagement. So what is special
about \emph{showing}? Hence, our research question is:

\vspace{-.2cm}
\begin{quote}
(Q2.7) Are passages of \emph{showing} special with regard to the way
of the imaginings they prescribe?
\end{quote}
\vspace{-.2cm}

\noindent The first two parts of the subproject identify a number of problems and
research questions which have implications for the very notion of
prescribed imaginings. Spelling out these implications, and arguing for
their relevance to a general theory of prescriptions to imagine in the
context of fiction constitutes \textbf{part three} of the subproject,
which will be conducted in close cooperation with the {first subproject
on foundational matters}.

 If the picture of literary interpretation sketched above is correct,
then it might turn out that prescriptions to imagine do not issue from
works of fiction \emph{tout court} but need to be construed as being
somehow sensitive to types of interpretation. (We can think of an
interpretation that seeks to promote intrinsically valuable experiences
and `historical interpretation' as two types of interpretation here).
This gives rise to the following research question:

\vspace{-.2cm}
\begin{quote}
(Q2.8)  Are prescriptions to imagine sensitive to types of
interpretation, and if so, how?
\end{quote}
\vspace{-.2cm}

\noindent There are at least three \emph{prima facie} options to answer this
question (cf. Lamarque 1996, 64): Firstly, what a work \emph{W}
prescribes to imagine could be said to have no unconditional validity,
but may be represented as `hypothetical imperatives': `When you engage
in an interpretation of type \emph{T} of \emph{W}, then you are
prescribed to imagine \emph{\ldots} by \emph{W}'. It is, however,
unclear whether all prescriptions to imagine have this hypothetical form
or only some. In other words, do we have different kinds of
prescriptions to imagine in the appreciation of literary fictions, some
with unconditional force and others conditional upon types of
interpretation? Secondly, we might opt for the de-emphasis of prescribed
imaginings that are not `apt' to a particular type of interpretation
\emph{T}, in the context of engaging in a \emph{T}-type interpretation.
Walton recommends to de-emphasize fictional facts that do not fit into
certain games of make-believe, meaning that there is a prescription to
imagine in these cases, but we somehow do not take it seriously (Walton
1990, 182). This strategy does not touch the unconditional force of
prescriptions to imagine. However, it rearranges the relation of
interpretation and prescriptions to imagine considerably, for
interpretations here do not only aim at determining prescriptions to
imagine, but also at their evaluation. As a third strategy, we might opt
for a `disjunction', claiming that work \emph{W} may have different
story worlds \emph{SW\textsubscript{1}, SW\textsubscript{2}, \ldots},
where each \emph{SW} depends on the type of interpretation \emph{T}
adopted. In this picture, prescriptions to imagine have unconditional
validity but are relativized to types of interpretation. The pros and
cons of these alternatives need to be evaluated, and they need to be
supplemented by further options. 

In our exposition of part two of the current subproject, we have
considered three examples of narrative-structural features that seem to
have an influence on the way of imagining that is prescribed by works of
fiction. The notion of `way' here refers to a mixed bag of phenomena:
\emph{\`a propos} unreliable narration, we have considered the notion of
imagining in an emotionally qualified way (such that we, say, are
invited to \emph{confidently} imagine that the protagonist escapes) as
well as the distinction between \emph{prima facie} and
all-things-considered prescriptions, and the idea that imaginings may be
supported with different strengths of reasons. \emph{|`A propos} the
narrative modes of internal focalization and showing (vs. telling), we
have considered the ways of imagining something from a character's
perspective, or imagining something in a vivid manner. Our final
research question, then, generalizes over the particularities of these
cases:

\vspace{-.2cm}
\begin{quote}
(Q2.9) How do prescriptions to imagine extend beyond the content of
what is to be imagined to the  \emph{way} of imagining?
\end{quote}
\vspace{-.2cm}
